Figure 6. Differential Protein expression

### 2022-09-30 reports/manuscript/Figure6.Rmd
Add scale legend

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(readxl)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

# top_PROT_mfi <- t
# gr <- "Luminal_gr"
# plot_heatmap.fun(t, "Luminal_gr", scale = T)
plot_heatmap.fun <- function(top_PROT_mfi, gr, scale = FALSE, layout = "none"){
  df <- na.omit(metadata[sample_use, c(gr, "ID")])
  df <- arrange(df, df[1])
  samples <- df[, "ID"]
  names(samples) <- df[, gr]

@@

    if(gr == "Tissue_gr") {
      height <-1.5 
      add_letter("c")
    }else{height <- round(max(h$height))
      add_letter("a")}
    #lines(x=c(0,height), y=c(0.45,0.45), col="black", lty=1, lwd = 2.5) # only for grob

>>>>

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(readxl)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

# top_PROT_mfi <- t
# sacale = T
# gr <- "Luminal_gr"
# plot_heatmap.fun(t, "Luminal_gr", scale = T)
plot_heatmap.fun <- function(top_PROT_mfi, gr, scale = FALSE, layout = "none"){
  df <- na.omit(metadata[sample_use, c(gr, "ID")])
  df <- arrange(df, df[1])
  samples <- df[, "ID"]
  names(samples) <- df[, gr]

@@

    if(gr == "Tissue_gr") {
      height <-1.5 
      add_letter("c")
    }else{
      add_scale_legend(x = par("usr")[1]-0.1, height = 1.5,#diff(par("usr")[3:4])-20,
                     pal = colorRampPalette(c("navy","grey95","firebrick"))(91),
                     labels = c("-5","0","5"))
      height <- round(max(h$height))
      add_letter("a")}
    #lines(x=c(0,height), y=c(0.45,0.45), col="black", lty=1, lwd = 2.5) # only for grob
